% HuffmanCoding.tex
\documentclass[12pt,letterpaper]{letter}
\usepackage{fullpage,color}
\usepackage[procnames]{listings}
\pagenumbering{gobble}

\newcommand{\assignment}{Huffman Coding\\}
\newcommand{\myinfo}{Darin Critchlow\\CSIS 2430-001}
\newcommand{\assignmentDescription}
{
Implement Huffman Coding
\begin{enumerate}\setlength\itemindent{0.5cm}
{
\item Use this file: Metamorphosis.txt
\item Convert the file to binary and measure the size.
\item Implement Huffman Coding to compress the file. (You will calculate the frequencies of all punctuations, etc., build a tree, then use the tree to compress the file (remember, it will be in BINARY - LEAVE IT in this format.)
\item Measure the newly compressed file.
\item Answer the question: What is the delta shrinkage (Entropy) from the first file to the second?
\item Use the frequencies found on page 771 \#27 and reimplement.
\item Measure the compression again.
\item Compare\//contrast (what did you find?, why was there much of a difference?, etc.)
}\end{enumerate}
}
\newcommand{\worked}{Everything worked properly}
\newcommand{\didntwork}{Everything worked properly}
\newcommand{\comments}
{
    As per our discussion in class, you need to follow these steps to make Huffman coding work as follows:
\begin{enumerate}
{
    \item As a baseline, make a copy of the Metamorphosis file and save it as a binary file.
    \item With your programming language, read in the file and calculate the frequency of all of the letters and characters (including spaces).
    \item Build your tree (good example in the book -- chapter 11.2?) from the frequencies.
    \item From your text file, use the tree you just created to recode the letters to the new variable bits from your tree in \#3 and save it as a second binary file.
    \item Compare binary file in \#1 to the one in \#4 and you should see a reduction (compression) of \emph{x}\%. Remember, all of your answers should be about the same within a small error.
}
\end{enumerate}
}

\begin{document}

\LARGE\textbf{\assignment{}}\\
\normalsize
\myinfo{}\\

\textbf{\underline{Objective:}}\\

\textbf{\assignmentDescription{}}

\textbf{\underline{What Worked:}}\\\\
\worked{}\\

\textbf{\underline{What Didn't Work:}}\\\\
\didntwork{}\\

\pagebreak
\textbf{\underline{Comments:}}\\\\
\comments{}

\pagebreak
\definecolor{keywords}{RGB}{255,127,0}
\definecolor{comments}{RGB}{169,169,169}
\definecolor{red}{RGB}{160,0,0}
\definecolor{green}{RGB}{46,139,87}

\lstset{language=Python,
        basicstyle=\ttfamily\small,
        keywordstyle=\color{keywords},
        commentstyle=\color{comments},
        stringstyle=\color{green},
        showstringspaces=false,
        identifierstyle=\color{black},
        procnamekeys={def,class}}
\textbf{\underline{Code:}}
\lstinputlisting[language=Python]{huffman.py}
\end{document}
